### 2025-09-08 README.qmd
update readme
updates of python code
updates of readme

---
output: github_document
---

@@

> Yi Zhe, Ben Marwick, Li Hao, Shuwen Pei (2025). Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)". Submitted to _Journal of Archaeological Science_

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. 
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations

>>>>

---
format: gfm
default-image-extension: ""
---

@@

> Ye Zhi, Ben Marwick, Li Hao, Shuwen Pei (2025). Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)". Submitted to _Journal of Archaeological Science_

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. 
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/paper/figures): Plots and other
    illustrations
  - [:file_folder: py_SPHARM](/py_SPHARM): Python source files for SPHARM analysis.  
    - **SPHARM_main**:  
        - `batch_operation.py` — batch calculation of spherical harmonics for STL files.  
        - `main.py` — shape analysis using spherical harmonics for a single STL file, including visualization of analysis results.  
    - **SPHARM_modules**: supporting modules for main scripts, including shape preprocessing, spherical harmonic computation/statistics, shape reconstruction, and computation/output of sphericity and curvature.
